\section{Background and the capability landscape}\label{sec:related}

The resilient-PNT comparison problem sits at the confluence of three well-developed
but separate tool ecosystems. Kshana does not displace any of them; it occupies the
intersection they leave open. We organise the landscape into three honest tiers and
make the boundaries explicit in Table~\ref{tab:intersection}.

\paragraph{Tier 1: quantum-navigation simulations.}
A growing body of work simulates quantum inertial and timing sensors, but almost
always from a quantum-specific, fusion-or-enhancement standpoint rather than as a
neutral quantum-versus-classical comparison harness. Atom-interferometric strapdown
navigation has been simulated end-to-end with a cold-atom accelerometer in the loop
\citep{atomstrapdown2023}, and high-fidelity simulators model the cold-atom
interferometer (CAI) at the level of fringe contrast and projection noise
\citep{quantumnav2025highfidelity}. We concede that the latter achieves
\emph{higher} fidelity than Kshana on the single inertial lever: its first-principles
CAI model is more detailed than our coefficient-driven projection. Hybrid
cold-atom/classical inertial estimation has likewise been demonstrated in an EKF
framework that fuses a CAI with a conventional IMU \citep{hybridcai2018}. These are
quantum-axis simulators; none provides a single neutral code path in which the same
scenario is run with a quantum or a classical sensor and the resilience figure of
merit compared like for like. The closest quantum-versus-classical service we are
aware of, TNO SENSED \citep{tno_sensed}, is closed and not reproducible: its
parameters, seeds and code are not publicly available, so its comparisons cannot be
independently re-derived. The field's own reviews note the absence of an open,
reproducible quantum-versus-classical comparison capability
\citep{coldatomnavreview2022,quantumpntreview2026}; in particular,
\citet{quantumpntreview2026} names no open reproducible quantum-versus-classical
PNT tool.

\paragraph{Tier 2: open navigation frameworks.}
Open, citable navigation frameworks already embody parts of the methodology we build
on. NaveGo \citep{gonzalez2017navego} establishes the interchangeable-error-model
pattern for inertial navigation -- a sensor is described by a parameter profile and
swapped without touching the estimator -- and we reuse its validated navigation-grade
IMU profiles as the classical baseline for the inertial lever. It has, however, no
quantum axis. Among open PNT and GNSS tools, LuPNT \citep{iiyama2023lupnt} is an
excellent, well-engineered library for lunar positioning, and gnss\_lib\_py
\citep{knowles2024gnsslibpy} is a similarly strong toolkit for real-data GNSS
analysis. We differentiate from these on the axes they do not target -- a
single-code-path quantum-versus-classical swap, and the reproducibility-triple
methodology (Section~\ref{sec:method}) -- and explicitly \emph{not} on engineering
quality, which in both cases is high. LuPNT is lunar-scoped; gnss\_lib\_py is oriented
to processing real observations rather than forward performance simulation.

\paragraph{Tier 3: astrodynamics and real-signal tools.}
The astrodynamics and real-signal ecosystem answers a fundamentally different
question. RTKLIB and comparable GNSS engines \citep{takasu2009} post-process real
pseudorange and carrier-phase observations to produce a position fix; GMAT
\citep{nasa_gmat} and Orekit \citep{orekit} are high-fidelity mission-design and
orbit-determination frameworks; the \code{sgp4} crate \citep{sgp4crate} is a
production analytic propagator; and Nyx with ANISE \citep{nyxanise} provides
DE-ephemeris-grade dynamics and serves in this work as a reference oracle, not a
rival. These tools consume real signals or drive high-fidelity mission analysis.
Kshana is primarily the upstream \emph{forward performance simulator}: it asks, for a
given scenario, seed and sensor parameterisation, how a resilience figure of merit
behaves, before any real observation exists. It does also close the
measurement-to-position loop with a code single-point-positioning path (real RINEX
observations to a receiver position, metre-level and validated on IGS data;
Section~\ref{sec:limitations}), but that is a boundary capability rather than the
carrier-phase precise positioning of a dedicated GNSS engine, and the engine's centre of
gravity remains forward simulation. In-browser SGP4 propagation is itself not new
\citep{satellitejs}; the delta here is a single engine running the full integrated
stack zero-install in WebAssembly, not the propagator alone.

To our knowledge, no open tool combines a single-code-path quantum-versus-classical
swap, seed-level reproducibility, and a terrestrial-plus-lunar resilience scope in one
deployable engine. Table~\ref{tab:intersection} states this symmetrically, listing the
axes Kshana lacks alongside those it has.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4pt}
\caption{Capability landscape across representative tools. Columns include axes that
Kshana lacks (three-axis INS mechanisation, raw-IQ spoofing) or supports only partially
(real-observation processing and a single-point-positioning fix) alongside axes it
provides outright (single-code-path quantum/classical swap, seed-level reproducibility,
terrestrial-plus-lunar resilience scope) and a deployment row. A checkmark ($\checkmark$)
denotes a supported capability, a parenthesised check (($\checkmark$)) a partial one, and
a dash (--) its absence: Kshana's real-observation and PVT support is \emph{code}
single-point positioning (metre-level, validated on IGS data), not carrier-phase PPP/RTK.
Kshana and RTKLIB still answer different questions: RTKLIB post-processes real signals
into a centimetre-grade carrier-phase position fix, whereas Kshana is primarily an
upstream forward performance simulator. The comparison is one of scope, not quality.}
\label{tab:intersection}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c c c c c c}
\toprule
& \rotatebox{90}{Quantum/classical}
& \rotatebox{90}{Seed-reproducible}
& \rotatebox{90}{Terr.+lunar resil.}
& \rotatebox{90}{Real-obs.\ proc.}
& \rotatebox{90}{PVT fix}
& \rotatebox{90}{3-axis INS mech.}
& \rotatebox{90}{Raw-IQ spoofing} \\
\midrule
Kshana \citep{baweja2026kshana}      & $\checkmark$ & $\checkmark$ & $\checkmark$ & ($\checkmark$) & ($\checkmark$) & --           & --           \\
LuPNT \citep{iiyama2023lupnt}        & --           & $\checkmark$ & --           & $\checkmark$ & $\checkmark$ & --           & --           \\
gnss\_lib\_py \citep{knowles2024gnsslibpy} & --     & $\checkmark$ & --           & $\checkmark$ & $\checkmark$ & --           & --           \\
NaveGo \citep{gonzalez2017navego}    & --           & $\checkmark$ & --           & --           & --           & $\checkmark$ & --           \\
RTKLIB \citep{takasu2009}            & --           & --           & --           & $\checkmark$ & $\checkmark$ & --           & --           \\
GMAT / Orekit \citep{nasa_gmat,orekit} & --         & --           & --           & $\checkmark$ & --           & --           & --           \\
TNO SENSED \citep{tno_sensed}        & $\checkmark$ & --           & --           & --           & --           & $\checkmark$ & --           \\
\code{sgp4} crate \citep{sgp4crate}  & --           & $\checkmark$ & --           & --           & --           & --           & --           \\
\bottomrule
\end{tabular}%
}

\vspace{0.4em}
{\small\emph{Deployment:} Kshana ships as a zero-install WebAssembly integrated
stack (the full pipeline in one engine), not as a single in-browser propagator.}
\end{table}
