\section{Validation}\label{sec:validation}

The trustworthiness of any comparison engine rests on whether its components
reproduce results that can be checked against an authority external to the
engine itself. Throughout this section we hold to a single discipline: every
number is compared against an external oracle (an independent reference
implementation, a published dataset, or an analytic closed form), and never
against Kshana's own output. We organise the evidence into three tiers ordered
by the strength of the external anchor, and we are explicit about what each tier
does and does not establish. Table~\ref{tab:validation} summarises the battery;
the prose below develops the caveats that the table can only flag.

\paragraph{Tier 1: bit-for-bit against an authoritative oracle.}
These checks reproduce an independent reference to within the numerical noise
floor, so agreement here speaks to correctness, not to a physical fit. The SGP4/SDP4 propagator reproduces all 666 verification states of
the AIAA 2006-6753 test set \citep{vallado2006} to a worst-case position error
of \SI{4.12}{\milli\metre} and velocity error of
\SI{1.85e-9}{\kilo\metre\per\second}. Against an independent Rust
implementation, the \code{sgp4} crate \citep{sgp4crate}, agreement is sub-micron
on the near-earth and resonant orbits and \SI{4.12}{\milli\metre} in the
worst case across all regimes; we therefore do not claim blanket sub-micron
agreement. The IAU~2000A nutation routine \code{eraNut00a} reproduces the SOFA
reference values $\Delta\psi = -0.96309\times10^{-5}$~rad and
$\Delta\epsilon = +0.40632\times10^{-4}$~rad to $10^{-13}$~rad
\citep{iausofa}. The frame transformations match the Vallado worked examples
\citep{vallado2006,iausofa} to \SI{0.1}{\milli\metre} (TEME$\rightarrow$PEF),
\SI{0.6}{\milli\metre} (TEME$\rightarrow$ITRF), and \SI{4}{\milli\metre} for the
full CIO-based GCRS$\rightarrow$ITRS chain. The Allan-deviation estimator
reproduces the Stable32/NBS14 reference series \citep{stable32,riley2008nist} to
a relative error of $10^{-4}$. The dilution-of-precision computation matches the
closed-form regular-tetrahedron geometry \citep{misra2010,kaplan2017} exactly:
$\mathrm{GDOP}=\sqrt{10}/2=1.5811$, $\mathrm{PDOP}=1.5$, $\mathrm{TDOP}=0.5$.
The inertial error model reproduces the velocity- and angle-random-walk
coefficients of the NaveGo 3DM-GX3-35 reference profiles
\citep{gonzalez2017navego} to within $5\%$. Finally, the two-body propagator
agrees with an independent universal-variable Kepler solver to sub-metre over
\SI{24}{\hour}, conserving energy and angular momentum to $\sim10^{-9}$
(relative). Tier~1 is the strongest evidence in the paper: each row is an
independent oracle, and the residuals are numerical, not physical.

\paragraph{Tier 2: post-fit residual against real agency truth.}
Tier~2 reports how closely Kshana's dynamics can be made to track precise
ephemerides published by space agencies. This is a \emph{force-model validation
by ephemeris fitting}, not orbit determination: there is no measurement
processing, and the residual is the post-fit overlap of a fitted trajectory
against the agency product. The arc length, gravity-field degree and order, and
empirical-acceleration tier are stated inline for every entry because they
determine what the residual means. Our headline is the Galileo MEO full-arc
result: a \SI{0.61}{\metre} post-fit residual over a \SI{24}{\hour} arc with a
degree/order-70 gravity field and no empirical accelerations, the configuration
that most directly exercises force-model fidelity. On the shorter \SI{8}{\hour} CI
arc the pure-force fit is \SI{0.13}{\metre}, and the reduced-dynamic tier, in
which per-revolution empirical accelerations are estimated alongside the
trajectory, lowers it further to \SI{0.07}{\metre}; the same reduced-dynamic tier
yields \SI{0.10}{\metre} for the Swarm-A LEO arc
\citep{montenbruck2000,petit2010iers}. We emphasise that these reduced-dynamic
numbers \emph{bound} force-model accuracy rather than measure it: the estimated
empirical accelerations absorb mismodelled dynamics, so a small reduced-dynamic
residual is an upper bound on, not a measurement of, the underlying force-model
error. They are reported as clearly-labelled secondary lines, never as the
headline.

The lunar case is stated as honestly as the favourable ones. The LRO arc yields
a \SI{6.6}{\metre} reduced-dynamic residual, which is \emph{above} our
\SI{5}{\metre} target \citep{lemoine2013grail,giorgini1996horizons}; we report
the miss rather than tuning it away. As a controlled cross-validation, we swap
the analytic kernel-free ephemeris for a DE440 realisation via ANISE: the LRO
reduced-dynamic residual is unchanged at the centimetre level
($6.65\rightarrow\SI{6.67}{\metre}$). This reproduces an established
result, that a carefully constructed analytic stack matches a DE-grade
ephemeris realisation for this class of arc \citep{bertone2021grail,li2023leopod};
it is not a discovery, and it is scoped to the LRO arc only. We credit
\code{nyx}/ANISE \citep{nyxanise} as the DE-grade oracle against which the swap
is checked, not as a rival the engine outperforms.

\paragraph{Tier 3: parameter-level characterisation.}
The multi-layer spoofing detector (per-epoch RAIM parity, automatic-gain-control
monitoring, signal-quality monitoring, and a fusion stage) is characterised
against the \emph{published scenario parameters} of the TEXBAT corpus
\citep{humphreys2012texbat}: the hand-coded inputs and expected outputs are
derived from the documented scenario descriptions. The detector ingests no
TEXBAT samples; raw-IQ ingestion is future work. We are explicit that this is
not external validation. Tier~3 establishes that the detection logic responds as
expected to parameter regimes drawn from a real corpus, but until raw IQ is
processed it cannot be called a validation against TEXBAT, and Table~\ref{tab:validation}
labels it accordingly.

\paragraph{Reading the table.}
The status vocabulary mirrors the methodology of Section~\ref{sec:method}.
Tier~1 rows are \emph{validated} against an external oracle to the numerical
floor. Tier~2 rows are \emph{validated by ephemeris fitting}: a genuine
external anchor (the agency product), but a fit, with the empirical-tier caveat
made explicit. Tier~3 is \emph{characterised, not validated}. None of these
rows involves a quantum figure of merit: the quantum-sensor performance models
are projections from cited device coefficients, treated in
Section~\ref{sec:crossover} and never entered into this external-validation
battery.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.25}
\caption{External-validation battery, tiered by the strength of the external
anchor. Every result is compared against an oracle independent of the engine.
Tier~1 reproduces an authoritative reference to the numerical floor; Tier~2
reports post-fit residuals against agency precise ephemerides (a force-model fit
by ephemeris fitting, with arc length, gravity degree/order, and
empirical-acceleration tier stated inline); Tier~3 is parameter-level
characterisation, not external validation. Reduced-dynamic residuals bound, and
do not measure, force-model accuracy.}
\label{tab:validation}
\begin{tabular}{@{}p{0.255\linewidth} p{0.215\linewidth} p{0.295\linewidth} p{0.155\linewidth}@{}}
\toprule
\textbf{Check} & \textbf{Oracle} & \textbf{Result} & \textbf{Status} \\
\midrule
\multicolumn{4}{@{}l}{\textit{Tier 1: bit-for-bit vs.\ authoritative oracle}}\\
\addlinespace[2pt]
SGP4/SDP4, 666 states &
AIAA 2006-6753 \citep{vallado2006} &
\SI{4.12}{\milli\metre} pos., \SI{1.85e-9}{\kilo\metre\per\second} vel.\ (worst case) &
Validated \\
SGP4 head-to-head &
\code{sgp4} crate \citep{sgp4crate} &
sub-\si{\micro\metre} near-earth/resonant; \SI{4.12}{\milli\metre} worst case all regimes &
Validated \\
Nutation \code{eraNut00a} &
SOFA/ERFA \citep{iausofa} &
$\Delta\psi=-0.96309\!\times\!10^{-5}$, $\Delta\epsilon=+0.40632\!\times\!10^{-4}$~rad to $10^{-13}$ &
Validated \\
Frame transforms &
Vallado \citep{vallado2006,iausofa} &
TEME$\to$PEF \SI{0.1}{\milli\metre}; TEME$\to$ITRF \SI{0.6}{\milli\metre}; GCRS$\to$ITRS \SI{4}{\milli\metre} &
Validated \\
Allan deviation &
Stable32/NBS14 \citep{stable32,riley2008nist} &
relative error $10^{-4}$ &
Validated \\
GDOP/PDOP/TDOP &
closed form \citep{misra2010,kaplan2017} &
$\sqrt{10}/2=1.5811$; $1.5$; $0.5$ (exact) &
Validated \\
Inertial VRW/ARW &
NaveGo 3DM-GX3-35 \citep{gonzalez2017navego} &
within $5\%$ &
Validated \\
Two-body propagation &
universal-variable Kepler &
sub-metre / \SI{24}{\hour}; energy + ang.\ mom.\ to $\sim10^{-9}$ &
Validated \\
\addlinespace[3pt]
\multicolumn{4}{@{}l}{\textit{Tier 2: post-fit residual vs.\ agency truth (force-model fit by ephemeris fitting)}}\\
\addlinespace[2pt]
Galileo MEO (headline) &
agency precise eph.\ \citep{montenbruck2000,petit2010iers} &
\SI{0.61}{\metre}, \SI{24}{\hour} arc, d/o~70, force-only &
Validated (fit) \\
Galileo MEO (\SI{8}{\hour}, reduced-dynamic) &
agency precise eph.\ \citep{montenbruck2000,petit2010iers} &
\SI{0.07}{\metre} (\SI{0.13}{\metre} pure-force); empirical-accel tier (bounds, not measures) &
Validated (fit) \\
Swarm-A LEO (reduced-dynamic) &
agency precise eph.\ \citep{montenbruck2000,petit2010iers} &
\SI{0.10}{\metre}; empirical-accel tier (bounds, not measures) &
Validated (fit) \\
LRO lunar &
GRGM \citep{lemoine2013grail,giorgini1996horizons} &
\SI{6.6}{\metre} reduced-dynamic, \emph{above} \SI{5}{\metre} target (honest miss) &
Validated (fit) \\
LRO DE440/ANISE swap &
\code{nyx}/ANISE \citep{nyxanise,bertone2021grail,li2023leopod} &
residual unchanged $6.65\!\to\!\SI{6.67}{\metre}$; reproduces known result, LRO-scoped &
Validated (fit) \\
\addlinespace[3pt]
\multicolumn{4}{@{}l}{\textit{Tier 3: parameter-level characterisation (not external validation)}}\\
\addlinespace[2pt]
Spoofing detector (RAIM + AGC + SQM + fusion) &
TEXBAT scenario \emph{parameters} \citep{humphreys2012texbat} &
responds as expected to documented parameter regimes; raw-IQ ingestion is future work &
Characterised, not validated \\
\bottomrule
\end{tabular}
\end{table}
