\section{Limitations and threats to validity}\label{sec:limitations}

The following disclosures form part of the honesty contract that the methodology
in Section~\ref{sec:method} demands. Every figure of merit is reported alongside the
strength of the evidence that backs it, and a result that is a model projection or a
force-model fit is never dressed as a measurement. The same discipline applies to the
boundaries of the engine itself.

\begin{itemize}

  \item \textbf{Quantum-sensor figures are projections, not measurements.}
  Every cold-atom inertial, optical-lattice clock, and optical time-transfer number
  in this paper (including the crossover and break-even results of
  Section~\ref{sec:crossover}) is a performance-model projection computed by
  deterministic arithmetic on coefficients drawn from the cited device literature
  \citep{templier2022,origlia2015,giorgetta2013,deschenes2016}, not data from
  operating hardware. We carry an inline maturity tag (flight-qualified /
  ground-lab / projection-floor) on every quantum point for exactly this reason
  (Figure~\ref{fig:clock}). For time transfer we keep the comparison like-for-like:
  the reported optical figure is charged with a conservative non-reciprocal
  differential-delay budget (a \SI{1}{\pico\second} on-orbit target, not the
  \SI{1}{\femto\second} laboratory floor), so it carries the same class of systematic
  that limits the RF figure (Section~\ref{sec:crossover}). A jitter-only optical floor
  would exclude that non-reciprocity and overstate the optical advantage; we do not
  report it.

  \item \textbf{The agency-orbit work is a force-model fit, not orbit
  determination.} The residuals against agency precise ephemerides
  (Table~\ref{tab:validation}) are obtained by \emph{force-model validation by ephemeris
  fitting} (propagation-overlap consistency against an external truth product), not by
  processing observations. The headline is the full-arc Galileo result,
  \SI{0.61}{\metre} over \SI{24}{\hour} at gravity-field degree/order~70. The
  reduced-dynamic tier on the \SI{8}{\hour} arc (Galileo \SI{0.07}{\metre} from a
  \SI{0.13}{\metre} pure-force fit, Swarm \SI{0.10}{\metre}) admits
  empirical accelerations that absorb mismodelled dynamics; these numbers
  \emph{bound}, and do not \emph{measure}, force-model accuracy, and we label them
  reduced-dynamic wherever they appear. The fits are single-satellite, single-day
  arcs; they are not a statistical population over regimes.

  \item \textbf{LRO is above the target.} The LRO reduced-dynamic
  residual is \SI{6.6}{\metre}, above our \SI{5}{\metre} target. Swapping the default
  ephemeris for a DE440/ANISE realisation leaves it essentially unchanged
  (\SI{6.65}{\metre} $\rightarrow$ \SI{6.67}{\metre}). We present this as a
  controlled reproduction of a known result \citep{bertone2021grail,li2023leopod},
  scoped to the LRO arc only and not a discovery, and we credit \texttt{nyx}/ANISE
  \citep{nyxanise} as the DE-grade oracle, not a rival the engine outperforms.

  \item \textbf{The spoofing detector does not ingest raw IQ.} It is characterised
  against published TEXBAT \emph{parameters} \citep{humphreys2012texbat} using
  hand-coded inputs and expected outputs; it does not read the TEXBAT recordings.
  Consequently we report no receiver-operating-characteristic curve and no
  $P_d$/$P_{fa}$ operating point. Raw-IQ ingestion is future work, and the detector
  sits in the not-externally-validated tier of Table~\ref{tab:validation}.

  \item \textbf{Single-point positioning is code-only, not carrier-phase
  PPP/RTK.} The engine spans the measurement-to-position gap with a code
  single-point-positioning solver: it ingests real RINEX pseudoranges and
  broadcast ephemeris and returns a receiver position by iterated weighted
  least squares (Sagnac and broadcast satellite-clock corrections, the
  dual-frequency L1/L2 ionosphere-free combination, and a Saastamoinen/Niell
  troposphere), recovering the surveyed coordinate of IGS station ABMF to
  \SI{5.7}{\metre} 3-D RMS (\SI{1.1}{\metre} horizontal). This is metre-level
  \emph{code} positioning, not carrier-phase precise positioning: there is no
  ambiguity resolution, carrier smoothing, or inter-epoch filter, so the
  centimetre-grade PPP/RTK domain remains that of dedicated tools such as RTKLIB
  \citep{takasu2009} (Table~\ref{tab:intersection}). The paper's central
  contribution is the resilience-comparison methodology of
  Section~\ref{sec:method}, not a competition on positioning accuracy, and this
  single-station code fix is a boundary capability rather than a member of the
  external-validation battery of Table~\ref{tab:validation}.

  \item \textbf{Modelling-fidelity defaults are deliberately modest.} The inertial
  mechanisation is 1-DOF, not a full 3-axis strapdown solution \citep{groves2013};
  atmospheric drag uses a static exponential density profile rather than NRLMSISE-00;
  solar radiation pressure is a cannonball model; relativity is Schwarzschild-only;
  and the default ephemerides are low-precision. Each is adequate for the
  comparison-under-uncertainty role and is overridden by the higher-fidelity paths
  only where a validation result requires it.

  \item \textbf{Time representation is single-\texttt{f64} Julian date.} A single
  double-precision Julian date gives roughly \SI{50}{\micro\second} resolution near
  the present epoch, which is immaterial for the resilience figures of merit reported
  here but would matter for sub-microsecond timing applications.

  \item \textbf{In-browser execution is a deployment property, not a capability.}
  Running the integrated stack zero-install in WASM lowers the barrier to
  reproduction; it does not extend what the engine computes. In-browser SGP4 is not
  itself new \citep{satellitejs}; the delta is a single engine running the full
  integrated stack with no installation.

\end{itemize}

\noindent Collectively these bounds define what the engine establishes: a
reproducible, falsifiable comparison framework with an external-validation battery
behind it. They equally define what it does not: it is not a measurement
campaign, not an orbit-determination system, and not a fielded quantum-sensing
result.
